The Gender Pay Gap in the General Social Survey

### 2023-08-30 Paper/paper.Rmd
Paper: Evaluation added

Perform a ridge regression to predict real incomes yields an RMSE of 26,062.58.

@@

>>>>

Performing a ridge regression to predict real incomes yields an RMSE of 26,062.58.

@@

# Evaluation

The aim of this paper is to predict individuals' wages. In order to evaluate the best prediction method we use the RMSE. The following table demonstrates the RMSE for each used method: \medskip

\begin{tabular}{l c} 
\textbf{Method} & \textbf{RMSE} \\ 
Linear Regression & 25,506.05 \\ 
Logistic Regression & 25,909.82 \\ 
Ridge & 26,062.58 \\ 
Lasso & 25,918.25 \\
Elastic Net & 25,918.81 \\ 
Random Forest & 31,745.54 \\ 
Gradient Boosting & 29,207.55 \\ 
\end{tabular}

\medskip
Conclusively, the linear regression yields the lowest RMSE and thus appears to be the best prediction method. Still, it delivers negative predictions of the wage. Therefore, we prefer the logistic regression as the best prediction method.

### 2023-08-30 Paper/paper.tex
Paper: Evaluation added

{[}Write something about cross validation?{]}

@@

>>>>

Furthermore, we use cross validation (CV) to assess the performance of a
model and to select appropriate hyperparameters. CV prevents overfitting
and helps in model selection.

@@

\hypertarget{evaluation}{%
\section{Evaluation}\label{evaluation}}

The aim of this paper is to predict individuals' wages. In order to
evaluate the best prediction method we use the RMSE. The following table
demonstrates the RMSE for each used method: \medskip

\begin{tabular}{l c} 
\textbf{Method} & \textbf{RMSE} \\ 
Linear Regression & 25,506.05 \\ 
Logistic Regression & 25,909.82 \\ 
Ridge & 26,062.58 \\ 
Lasso & 25,918.25 \\
Elastic Net & 25,918.81 \\ 
Random Forest & 31,745.54 \\ 
Gradient Boosting & 29,207.55 \\ 
\end{tabular}

\medskip

Conclusively, the linear regression yields the lowest RMSE and thus
appears to be the best prediction method. Still, it delivers negative
predictions of the wage. Therefore, we prefer the logistic regression as
the best prediction method.
